Results

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
comments and 2 letters
added rm before ANOVA

Data collection took place between 16th of August 2022 and the 3rd of February 2023.
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M\text{ }\pm\text{ }SD =`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }`r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$ years old), which is `r format(round((sum(data_survey[,"followup_ered_complete"] == 2)-1)/85, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

@@

### Manipulation checks

#### Subjective arousal and physiological responding

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```

@@

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$

The second model explained `r papaja::printnum(MLM2_r2[2]*100, digits=1)`% of variance. 
All results of the second model are in Table\ \@ref(tab:TabMLMH5).

@@

``` {r TabMLMH5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H",
  digits = 3)
```

The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.
The effect sizes of all other predictors were negligibly small ($f^{2}< 0.01$).

@@

```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block. Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block. The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05. $N=120$". Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license., fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
```

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`. <!-- hier wird "2022-08 and 2023-02" geschrieben, finde ich im Lesefluss nicht so schön. Wie wäre es mit "August 2022 and February 2023"?-->
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

@@

### Manipulation checks <!-- es gibt keine weitere Überschrift auf dieser Ebene, würde ich jedoch erwarten.-->

#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence on arousal and facial EMG." -->

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity. <!-- in den Methods habt ihr es klein und kursiv geschrieben. -->
Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```

@@

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$

The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
All results of the second model are in Table\ \@ref(tab:TabMLMH5).

@@

``` {r TabMLMH5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```

The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.
The effect sizes of all other predictors were negligibly small ($f^{2}< 0.01$).

@@

```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block. Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block. $N=120$", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
```

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
